An analysis of underlying relationships between factors related to operating costs and revenue in Australian vineyards.

### 2023-11-21 article.tex
summary tables

\subsection{Data}
% 6091 samples - total
% 58 regions
% 10 years
% 
% 853 with reported profits
% 46 regions
% reported since 2018
Data used in this analysis were obtained from Sustainable Winegrowing Australia. Australia's national wine industry sustainability program. The program aims to support grape-growers and winemakers in demonstrating and improving their sustainability \citep{swaSustainableWingrowingAustralia2022}. Data recorded by SWA are entered manually by winegrowers using a web based interface tool. A total of 6091 observations were collected from 2012/2013 to 2021/2022 financial years, with each observation comprising 23 variables reflecting a vineyard's state for the given year (see Table \ref{tab:vars}). 
\par
\begin{table}[] 
 \label{tab:vars}
 \caption{Summary of variables used in the analysis. The recorded column indicate the number of values that were either greater than zero or that were not missing.}\label{tab:summary}
 \begin{tabular}{@{}ccccl@{}}
  \toprule
  \textbf{Variable} & \textbf{Units} & \textbf{Recorded} & \textbf{\begin{tabular}[c]{@{}c@{}}Number of\\ Classes\end{tabular}} & \\ \midrule
  Water Used & Mega Litres & 5846 & & \\
  Diesel & Litres & 5585 & & \\
  Biodiesel & Litres & 25 & & \\
  LPG & Litres & 958 & & \\
  Herbicide Spray & Times per year & 2026 & & \\
  Year & Class & 6091 & 10 & \\
  Disease & Class & 6091 & 2 & \\
  Region & Class & 6091 & 58 & \\
  Solar & Kilowatt Hours & 622 & & \\
  Irrigation Type & Class & 6091 & 20 & \\
  Petrol & Litres & 4309 & & \\
  Slashing & Times per year & 2290 & & \\
  Yield & Tonnes & 5935 & & \\
  Irrigation Energy & Class & 6091 & 16 & \\
  Area Harvested & Hectares & 6091 & & \\
  Electricity & Kilowatt Hours & 1015 & & \\
  Insecticide Spray & Times per year & 1092 & & \\
  Fertiliser & \begin{tabular}[c]{@{}c@{}}Kilograms \\ of Nitrogen\end{tabular} & 795 & & \\
  Fungicide Spray & Times per year & 2260 & & \\
  Cover Crop & Class & 6091 & 32 & \\
  Water Type & Class & 6091 & 39 & \\
  Grape Revenue & AUD & 853 & & \\
  Operating Costs & AUD & 853 & & \\ \bottomrule
  \end{tabular}
\end{table}
% FIXME: Add supplementary tables of all classes and another table of the summary statistics of continuous variables. Refer to this table to help with the paragraphs about one-hot encoding. A quick definition of one-hot encoding will also help!
The data originally contained only two multiclass variables: year and region. Variables that measured the same metric from different sources (such as water collected from rivers versus water from dams) were converted into multiclass variables representing the source through one-hot-encoding. Changing each variable class into a binary value, with one indicating the presence of the class and zero indicating its absence. Occurrences of multiple sources were defined as their own separate classes. Where a class variable had a recorded amount the total amount used from these variables was retained as a separate variable; for example water used (in Mega Litres ) was also included alongside water source.
\par
The variable region represented one of the 65 Geographical Indicator Regions (GI Region) used to describe different unique localised traits of vineyards across Australia \citep{hallidayAustralianWineEncyclopedia2009,oliverReviewSoilPhysical2013,soarClimateDriversRed2008}. Each region is explicitly defined under the Wine Australia Corporation Act of 1980 \citep{attorney-generalsdepartmentWineAustraliaCorporation2010}.
\par

@@

>>>>

\subsection{Data}
% 6049 samples - total
% 58 regions
% 10 years
% 
% 853 with reported profits
% 46 regions
% reported since 2018
Data used in this analysis were obtained from Sustainable Winegrowing Australia. Australia's national wine industry sustainability program. The program aims to support grape-growers and winemakers in demonstrating and improving their sustainability \citep{swaSustainableWingrowingAustralia2022}. Data recorded by SWA are entered manually by winegrowers using a web based interface tool. A total of 6049 observations were collected from 2012/2013 to 2021/2022 financial years, with each observation comprising 23 variables reflecting a vineyard's state for the given year (see Table \ref{tab:vars}). 
\par
\begin{table}[] 
 \label{tab:vars}
 \caption{Summary of variables used in the analysis. The recorded column indicate the number of values that were either greater than zero or that were not missing.}\label{tab:summary}
 \begin{tabular}{@{}ccccl@{}}
  \toprule
  \textbf{Variable} & \textbf{Units} & \textbf{Recorded} & \textbf{\begin{tabular}[c]{@{}c@{}}Number of\\ Classes\end{tabular}} & \\ \midrule
  Water Used & Mega Litres & 5846 & & \\
  Diesel & Litres & 5585 & & \\
  Biodiesel & Litres & 25 & & \\
  LPG & Litres & 958 & & \\
  Herbicide Spray & Times per year & 2026 & & \\
  Year & Class & 6049 & 10 & \\
  Disease & Class & 6049 & 2 & \\
  Region & Class & 6049 & 58 & \\
  Solar & Kilowatt Hours & 622 & & \\
  Irrigation Type & Class & 6049 & 20 & \\
  Petrol & Litres & 4309 & & \\
  Slashing & Times per year & 2290 & & \\
  Yield & Tonnes & 5935 & & \\
  Irrigation Energy & Class & 6049 & 16 & \\
  Area Harvested & Hectares & 6049 & & \\
  Electricity & Kilowatt Hours & 1014 & & \\
  Insecticide Spray & Times per year & 1092 & & \\
  Fertiliser & \begin{tabular}[c]{@{}c@{}}Kilograms \\ of Nitrogen\end{tabular} & 795 & & \\
  Fungicide Spray & Times per year & 2260 & & \\
  Cover Crop & Class & 6049 & 32 & \\
  Water Type & Class & 6049 & 39 & \\
  Grape Revenue & AUD & 853 & & \\
  Operating Costs & AUD & 853 & & \\ \bottomrule
  \end{tabular}
\end{table}
% FIXME: Add supplementary tables of all classes and another table of the summary statistics of continuous variables. Refer to this table to help with the paragraphs about one-hot encoding. A quick definition of one-hot encoding will also help!
The data originally contained only two multiclass variables: year and region. Variables that measured the same metric from different sources (such as water collected from rivers versus water from dams) were converted into multiclass variables representing the source through one-hot-encoding. Changing each variable class into a binary value, with one indicating the presence of the class and zero indicating its absence. Occurrences of multiple sources were defined as their own separate classes. Where a class variable had a recorded amount the total amount used from these variables was retained as a separate variable; for example water used (in Mega Litres ) was also included alongside water source.
\par
The variable region represented one of the 65 Geographical Indicator Regions (GI Region) used to describe different unique localised traits of vineyards across Australia \citep{hallidayAustralianWineEncyclopedia2009,oliverReviewSoilPhysical2013,soarClimateDriversRed2008}. Each region is explicitly defined under the Wine Australia Corporation Act of 1980 \citep{attorney-generalsdepartmentWineAustraliaCorporation2010}.
\par

@@

 \section{Variable summaries}

The Table \ref{cont_summary} below shows the ranges of each of the continuous variables:
% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
  \begin{tabular}{@{}lllllllll@{}}
  \toprule
   & count & mean & std & min & 0.25 & 0.5 & 0.75 & max \\ \midrule
  Vineyard Solar & 622 & 22916.89 & 104808 & 1 & 1170.75 & 5500 & 14866.25 & 2300000 \\
  Biodiesel & 25 & 6635.932 & 11768.832104 & 1 & 200 & 500 & 10000 & 37216 \\
  Fungicide Spray & 2260 & 7.724801 & 3.279794 & 1 & 6 & 7 & 9 & 68 \\
  LPG & 958 & 327.831399 & 861.538804 & 1 & 40 & 95.835 & 240 & 11950 \\
  Petrol & 4309 & 825.276809 & 1556.621119 & 1 & 135 & 306.66 & 903 & 38568 \\
  Insecticide Spray & 1092 & 1.707189 & 1.316042 & 0 & 1 & 1 & 2 & 12 \\
  Water Used & 5846 & 7301838 & 558206600 & 0.0007 & 13.2655 & 43 & 146.875 & 42680000000 \\
  Fertiliser & 795 & 91149.89 & 483913.4 & 1 & 560 & 4759.5 & 45148.5 & 11358000 \\
  Diesel & 5585 & 11677.070183 & 24380.588742 & 0.1267 & 1240 & 3850 & 12500 & 591000 \\
  Yield & 5935 & 772.902449 & 2175.113895 & 0.03 & 68 & 192.3 & 601.8795 & 72305 \\
  Herbicide Spray & 2026 & 2.646199 & 2.598899 & 0 & 2 & 2 & 3 & 103 \\
  Slashing & 2290 & 3.311485 & 1.826788 & 1 & 2 & 3 & 4 & 26 \\
  Electricity & 1014 & 58223.07 & 177626.3 & 0.019 & 2160 & 9637 & 36498.25 & 3000000 \\
  Area Harvested & 6049 & 66.52604 & 133.4525 & 2.220446E-16 & 10.13 & 24.5 & 66.8 & 2436.15 \\
  Grape Revenue & 875 & 377972 & 606286.8 & 1 & 76000 & 172964 & 386747 & 5700000 \\
  Operating Costs & 853 & 314187.1 & 511522.6 & 1 & 57315 & 140000 & 327408 & 4482828 \\ \bottomrule
  \end{tabular}
  \end{table}

  \section{water types}
  % Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
  \begin{tabular}{@{}ll@{}}
  \toprule
  water types & frequency \\ \midrule
  river water & 1578 \\
  groundwater & 1433 \\
  surface water dam & 617 \\
  recycled water from other source & 386 \\
  groundwater and surface water dam & 256 \\
  not listed & 235 \\
  mains water & 170 \\
  river water and groundwater & 147 \\
  groundwater and recycled water from other source & 145 \\
  other water & 101 \\
  river water and surface water dam & 92 \\
  groundwater and water applied for frost control & 90 \\
  groundwater and mains water & 76 \\
  river water and groundwater and  surface water dam & 70 \\
  recycled water from other source and mains water & 63 \\
  groundwater and recycled water from other source and mains water & 60 \\
  river water and mains water & 57 \\
  surface water dam and mains water & 56 \\
  groundwater and other water & 33 \\
  river water and groundwater and mains water & 30 \\
  groundwater and surface water dam and recycled water from other source & 27 \\
  river water and water applied for frost control & 27 \\
  groundwater and surface water dam and mains water & 22 \\
  surface water dam and recycled water from other source & 21 \\
  river water and recycled water from other source & 19 \\
  river water and other water & 19 \\
  river water and surface water dam and mains water & 18 \\
  river water and groundwater and surface water dam and mains water & 18 \\
  mains water and other water & 16 \\
  groundwater and surface water dam and water applied for frost control & 12 \\
  surface water dam and other water & 12 \\
  groundwater and recycled water from other source and other water & 11 \\
  groundwater and surface water dam and recycled water from other source and mains water & 8 \\
  recycled water from other source and mains water and other water & 8 \\
  river water and recycled water from other source and mains water & 8 \\
  river water and surface water dam and recycled water from other source & 8 \\
  surface water dam and mains water and other water & 7 \\
  recycled water from other source and other water & 7 \\
  river water and groundwater and recycled water from other source & 6 \\
  groundwater and mains water and other water & 5 \\
  groundwater and surface water dam and other water & 5 \\
  groundwater and surface water dam and mains water and other water & 5 \\
  river water and groundwater and recycled water from other source and mains water & 5 \\
  river water and groundwater and water applied for frost control & 5 \\
  river water and surface water dam and water applied for frost control & 4 \\
  surface water dam and water applied for frost control & 4 \\
  river water and groundwater and surface water dam and recycled water from other source and mains water and other water & 4 \\
  river water and groundwater and recycled water from other source and other water & 3 \\
  groundwater and surface water dam and recycled water from other source and water applied for frost control & 3 \\
  river water and groundwater and surface water dam and recycled water from other source & 3 \\
  river water and recycled water from other source and other water & 3 \\
  surface water dam and recycled water from other source and mains water & 2 \\
  river water and recycled water from other source and mains water and water applied for frost control & 2 \\
  groundwater and surface water dam and recycled water from other source and mains water and other water & 2 \\
  river water and groundwater and mains water and other water & 2 \\
  river water and groundwater and surface water dam and other water & 2 \\
  river water and surface water dam and other water & 2 \\
  river water and mains water and water applied for frost control & 2 \\
  river water and groundwater and surface water dam and recycled water from other source and mains water & 2 \\
  river water and mains water and other water & 2 \\
  river water and surface water dam and mains water and other water & 2 \\
  river water and groundwater and mains water and water applied for frost control & 1 \\
  surface water dam and other water and water applied for frost control & 1 \\
  water applied for frost control & 1 \\
  groundwater and other water and water applied for frost control & 1 \\
  other water and water applied for frost control & 1 \\
  groundwater and surface water dam and recycled water from other source and other water and water applied for frost control & 1 \\
  mains water and water applied for frost control & 1 \\
  groundwater and surface water dam and recycled water from other source and other water & 1 \\
  groundwater and mains water and water applied for frost control & 1 \\
  river water and groundwater and surface water dam and mains water and other water & 1 \\
  river water and surface water dam and recycled water from other source and mains water & 1 \\ \bottomrule
  \end{tabular}
  \end{table}

\section{cover crop types}
% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
  \begin{tabular}{@{}ll@{}}
  \toprule
  Cover crop types & frequency \\ \midrule
  permanent_cover_crop_volunteer_sward & 1822 \\
  permanent_cover_crop_non_native & 936 \\
  permanent_cover_crop_native & 490 \\
  annual_cover_crop & 479 \\
  groundwater and surface water dam & 406 \\
  annual_cover_crop and permanent_cover_crop_volunteer_sward & 309 \\
  bare_soil & 225 \\
  permanent_cover_crop_non_native and permanent_cover_crop_volunteer_sward & 214 \\
  annual_cover_crop and permanent_cover_crop_non_native & 169 \\
  bare_soil and permanent_cover_crop_volunteer_sward & 129 \\
  bare_soil and permanent_cover_crop_non_native & 115 \\
  annual_cover_crop and permanent_cover_crop_non_native and permanent_cover_crop_volunteer_sward & 101 \\
  bare_soil and annual_cover_crop & 93 \\
  permanent_cover_crop_native and permanent_cover_crop_volunteer_sward & 80 \\
  bare_soil and permanent_cover_crop_native & 78 \\
  annual_cover_crop and permanent_cover_crop_native & 78 \\
  permanent_cover_crop_native and permanent_cover_crop_non_native & 68 \\
  permanent_cover_crop_native and permanent_cover_crop_non_native and permanent_cover_crop_volunteer_sward & 44 \\
  annual_cover_crop and permanent_cover_crop_native and permanent_cover_crop_non_native and permanent_cover_crop_volunteer_sward & 44 \\
  bare_soil and annual_cover_crop and permanent_cover_crop_volunteer_sward & 33 \\
  bare_soil and permanent_cover_crop_non_native and permanent_cover_crop_volunteer_sward & 26 \\
  annual_cover_crop and permanent_cover_crop_native and permanent_cover_crop_volunteer_sward & 17 \\
  bare_soil and annual_cover_crop and permanent_cover_crop_native & 15 \\
  annual_cover_crop and permanent_cover_crop_native and permanent_cover_crop_non_native & 15 \\
  bare_soil and annual_cover_crop and permanent_cover_crop_non_native & 13 \\
  bare_soil and annual_cover_crop and permanent_cover_crop_native and permanent_cover_crop_non_native and permanent_cover_crop_volunteer_sward & 12 \\
  bare_soil and annual_cover_crop and permanent_cover_crop_non_native and permanent_cover_crop_volunteer_sward & 11 \\
  bare_soil and annual_cover_crop and permanent_cover_crop_native and permanent_cover_crop_non_native & 8 \\
  bare_soil and permanent_cover_crop_native and permanent_cover_crop_non_native & 7 \\
  bare_soil and permanent_cover_crop_native and permanent_cover_crop_volunteer_sward & 6 \\
  bare_soil and permanent_cover_crop_native and permanent_cover_crop_non_native and permanent_cover_crop_volunteer_sward & 4 \\
  bare_soil and annual_cover_crop and permanent_cover_crop_native and permanent_cover_crop_volunteer_sward and & 2 \\ \bottomrule
  \end{tabular}
  \end{table}

\section{irrigation type}

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
  \begin{tabular}{@{}ll@{}}
  \toprule
  Irrigation type & frequency \\ \midrule
  dripper & 4800 \\
  dripper and non_irrigated & 342 \\
  Not listed & 319 \\
  dripper and overhead_sprinkler & 201 \\
  dripper and undervine_sprinkler & 91 \\
  non_irrigated & 65 \\
  undervine_sprinkler & 53 \\
  dripper and flood & 53 \\
  overhead_sprinkler & 46 \\
  dripper and overhead_sprinkler and undervine_sprinkler & 28 \\
  overhead_sprinkler and undervine_sprinkler & 12 \\
  dripper and non_irrigated and overhead_sprinkler & 11 \\
  flood and undervine_sprinkler & 10 \\
  dripper and flood and undervine_sprinkler & 7 \\
  dripper and flood and non_irrigated and overhead_sprinkler and undervine_sprinkler & 3 \\
  dripper and flood and overhead_sprinkler & 3 \\
  non_irrigated and undervine_sprinkler & 2 \\
  dripper and flood and non_irrigated & 1 \\
  dripper and non_irrigated and overhead_sprinkler and undervine_sprinkler & 1 \\
  flood and & 1 \\ \bottomrule
  \end{tabular}
  \end{table}

  \section{irrigation energy type}

  % Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
  \begin{tabular}{@{}ll@{}}
  \toprule
  Irrigation energy type & frequency \\ \midrule
  electricity & 2162 \\
  not listed & 2053 \\
  pressure & 586 \\
  electricity and pressure & 396 \\
  diesel & 254 \\
  diesel and electricity & 227 \\
  electricity and solar & 96 \\
  diesel and electricity and pressure & 90 \\
  diesel and pressure & 74 \\
  solar & 50 \\
  electricity and pressure and solar & 23 \\
  diesel and electricity and solar & 14 \\
  diesel and electricity and pressure and solar & 10 \\
  pressure and solar & 9 \\
  diesel and solar & 4 \\
  diesel and pressure and solar and & 1 \\ \bottomrule
  \end{tabular}
  \end{table}

  \section{year}
  % Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
  \begin{tabular}{@{}ll@{}}
  \toprule
  data_year_id & frequency \\ \midrule
  2021/2022 & 954 \\
  2020/2021 & 860 \\
  2019/2020 & 599 \\
  2012/2013 & 590 \\
  2013/2014 & 549 \\
  2015/2016 & 548 \\
  2014/2015 & 505 \\
  2017/2018 & 493 \\
  2016/2017 & 485 \\
  2018/2019 & 466 \\ \bottomrule
  \end{tabular}
  \end{table}

\section{giregion}
% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
  \begin{tabular}{@{}ll@{}}
  \toprule
  giregion & frequency \\ \midrule
  McLaren Vale & 1195 \\
  Barossa Valley & 584 \\
  Murray Darling & 521 \\
  Riverland & 472 \\
  Adelaide Hills & 454 \\
  Langhorne Creek & 347 \\
  Margaret River & 344 \\
  Coonawarra & 284 \\
  Padthaway & 202 \\
  Wrattonbully & 195 \\
  Clare Valley & 149 \\
  Yarra Valley & 122 \\
  Eden Valley & 92 \\
  Tasmania & 89 \\
  Swan Hill & 83 \\
  Grampians & 73 \\
  Orange & 72 \\
  Hunter Valley & 70 \\
  Bendigo & 53 \\
  Great Southern & 51 \\
  Rutherglen & 41 \\
  Robe & 36 \\
  Tumbarumba & 35 \\
  Mornington Peninsula & 32 \\
  King Valley & 32 \\
  Southern Fleurieu & 30 \\
  Heathcote & 29 \\
  Adelaide Plains & 25 \\
  Currency Creek & 24 \\
   & 23 \\
  Henty & 22 \\
  Canberra District & 21 \\
  Southern Flinders Ranges & 20 \\
  Upper Goulburn & 20 \\
  Mudgee & 20 \\
  Mount Benson & 20 \\
  Other & 19 \\
  Riverina & 18 \\
  Alpine Valleys & 15 \\
  Barossa Zone & 14 \\
  Pemberton & 12 \\
  Mount Gambier & 11 \\
  Blackwood Valley & 10 \\
  Kangaroo Island & 10 \\
  Big Rivers Zone Other & 9 \\
  Geographe & 7 \\
  Cowra & 6 \\
  Gundagai & 5 \\
  Strathbogie Ranges & 5 \\
  Glenrowan & 4 \\
  Geelong & 4 \\
  Swan District & 4 \\
  Goulburn Valley & 3 \\
  Beechworth & 3 \\
  Southern Highlands & 3 \\
  Macedon Ranges & 2 \\
  Pyrenees & 2 \\
  Sunbury & 1 \\ \bottomrule
  \end{tabular}
  \end{table}
